Anonymous provision of services via blockchain

### 2022-02-25 access.tex
submit work
update fairness analysis

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Anonymous provision of local services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some informations in a fairly manner, i.e., either both parties obtain the goods being exchanged, or they both obtain nothing.

@@

We contribute to the field of fair-exchanges by proposing a simple,
practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: 
our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

@@

\section{State of the art}\label{state-of-the-art}

\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for
Physical Products
Delivery}\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

\section{Background}
\subsection{Dispute resolution system}

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in section ~\ref{future-work}.

\subsection{Proofs to justice}\label{proof-of-justice}

@@

\subsection{Anonymity, pseudonomity, and confidentality}\label{pseudo-anonymous-vs-anonymous-blockchain}

@@

\section{The Protocol}

@@

\item Anonymous payments:
    \begin{itemize}
        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{pseudo-anonymous-vs-anonymous-blockchain}.
        \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
    \end{itemize}

@@

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{future-work}).

@@

\section{Fairness analysis}
We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.

@@

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-table-of-positions.png}
\centering
\caption{Formal table of positions}
\label{fig:positions}
\end{figure}

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = •\) - the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position (•). One would argue that the customer has put effort of
    delivering the materials to the SP, or that the sample is valuable.
    We assume that the sample without personal information is useless
    and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = •\) - the SP is in neutral position as
    he didn't put any effort to rece the package, also the package
    hasn't any value to the SP (•).
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{1, c, \mathrm{d}} = -\) - the customer lose the case as
    the SP has still opportunity to publish proof-of-provision within
    timeframe (-).
  \item
    \(\sigma_{1, s, \mathrm{d}} = •\) - the SP win the case for the same
    reason (•).
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{1, c, \mathrm{n}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{1, s, \mathrm{n}} = •\) or
  \(\sigma_{1, s, \mathrm{d}} = •\).
\end{itemize}

@@

@@

  \item
    \(\sigma_{2, c, \mathrm{n}} = -\) the customer has spend his funds
    but hasn't received the results. Therefore, he moves to the
    disadvantaged position (-).
  \item
    \(\sigma_{2, s, \mathrm{n}} = +\) the SP has received the payment
    but hasn't spend his resources yet. Therefore, he moves to advantaged
    position (+).
  \end{itemize}
\item
  Starting a dispute:

  \item
    \(\sigma_{2, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision before the
    deadline (-)
  \item
    \(\sigma_{2, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

Customer has timeouted \(time-to-issue-\), then:

  \item
    \(\sigma_{2, c, \overline{\mathrm{n}}} = •\) - the customer ends up
    in neutral position, since he didn't spend his funds (•)
  \item
    \(\sigma_{2, s, \overline{\mathrm{n}}} = •\) - The SP ends up in
    neutral position as he didn't receive the payment, nor spent his
    resources (•)
  \end{itemize}
\item
  Starting a dispute:

  \item
    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\) - the customer loses
    the case as he can not prove the payment before the time limit.
    Consequently, ends up in disadvantaged position (-)
  \item
    \(\sigma_{2, s, \overline{\mathrm{d}}} = •\) - the SP is not charged
    to the justice due to lack of proofs. Therefore, he ends up in
    neutral position (•)
  \end{itemize}
\end{itemize}

@@

\item
  The customer can move the protocol forward to the step 3, where if the
  SP follow the protocol then the customer can push the protocol forward
  up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
  otherwise if at any step the SP does not follow the protocol the
  customer can start a dispute which terminates the protocol at
  non-disadvantaged position, i.e.,
  \(\sigma_{3, c, \overline{\mathrm{d}}} = •\),
  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\),
  \(\sigma_{5, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
  \(\sigma_{2, s, \overline{\mathrm{n}}} = •\),
  \(\sigma_{2, s, \overline{\mathrm{d}}} = •\).
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{3, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe (-)
  \item
    \(\sigma_{3, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{4, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \mathrm{d}} = -\) the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe (-)
  \item
    \(\sigma_{4, s, \mathrm{d}} = +\) the SP win the case for the same
    reason (+)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in
  non-disadvantaged position
  \(\sigma_{4, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position (-).
  \item
    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fullfiled the contract
    on time (+).
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment (+)
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
    results but not the results. Therefore, he is still in disadvantaged
    position(-).
  \item
    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed(+).
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position (-)
  \item
    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment but didn't spend his
    resources (+)
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position (•)
  \item
    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position
  \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
  to non-disadvantaged termination position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
  the protocol start a dispute and win the case
  \(\sigma_{6, c, \overline{\mathrm{d}}} = •\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{6, s, \mathrm{n}} = +\), or
  \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
    results. Therefore, he moves to advantaged position (+).
  \item
    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed
    (+).
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision (-)
  \item
    \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision (+)
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in
    disadvantaged position, as he ends up with incorrect results (-)
  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
    position as he received the payment but didn't spend his resources
    (+)
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position (•)
  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position (-)
  \end{itemize}
\end{itemize}

@@

\section{Future work}\label{future-work}
\subsection{Justice}\label{justice}

@@

\section{Conclusions}
In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision. The framework can be employed by any local service provider to provide services without collecting any personal information. The payment is handled by anonymous cryptocurrencies. Proof of delivery and proof of provision are published on message board blockchain. The results are published on content addressable p2p network. The dispute can be settled by disclosing proofs to justice. Assuming the definition~\ref{fairness} we showed that the protocol achieve fairness. Finally, we pinpointed further improvements like decentralised dispute resolution, provable  availability of results, paying with cash, and anonymous delivery via courier.

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1}}

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some goods in a fairly manner, i.e., either both parties obtain the goods, or they both obtain nothing.

@@

\paragraph{Contributions}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonimity:
throughout the whole transaction the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivised to act accordingly to the protocol; otherwise the misbehaving party ends up in worst position.
\item Dispute resolution: at each step of the protocol the customer can open a dispute win the case iff the SP misbehaved.
\item TTP-less: 
our protocol does not rely on trusted-third party to conduct transactions in fairly manner. Only in case of dispute the centralised justice is invlolved (the justice decentralisation is discussed in section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

@@

\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:background} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in details.
Section~\ref{sec:fairness-analysis} provides an fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}

\paragraph{Anonymity and Fair-Exchange in e-Commerce Protocol for Physical Products Delivery} \label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

\section{Background}\label{sec:background}
\subsection{Dispute resolution system}

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in section ~\ref{sec:future-work}.

\subsection{Fairness}\label{proof-of-justice}

@@

\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}

@@

\section{The Protocol}\label{sec:protocol}

@@

\item Anonymous payments:
    \begin{itemize}
        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
        \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
    \end{itemize}

@@

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{sec:future-work}).

@@

\section{Fairness analysis}\label{sec:fairness-analysis}

We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.

@@

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-table-of-positions.png}
\centering
\caption{Table of positions after each step of protocol}
\label{fig:positions}
\end{figure}

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position. One would argue that the customer has put effort of
    delivering the materials to the SP, or that the sample is valuable.
    We assume that the sample without personal information is useless
    and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{1, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe.
  \item
    \(\sigma_{1, s, \mathrm{d}} = \sbullet\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
  \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
\end{itemize}

@@

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\sigma_{2, c, \mathrm{n}} = -\), the customer has spend his funds but hasn't received the results.
  \item
    \(\sigma_{2, s, \mathrm{n}} = +\), the SP has received the payment but hasn't spend his resources yet.
  \end{itemize}
\item
  Starting a dispute:

  \begin{itemize}
  \item
    \(\sigma_{2, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision before the deadline.
  \item
    \(\sigma_{2, s, \mathrm{d}} = +\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

Customer has time outed, then:

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\sigma_{2, c, \overline{\mathrm{n}}} = \sbullet\), the customer ends up in neutral position, since he didn't spend his funds.
  \item
    \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\), the SP ends up in neutral position as he didn't receive the payment, nor spent his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{2, c, \overline{\mathrm{d}}} = -\), the customer loses the case as he can not prove the payment before the time limit.
  \item
    \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\), the SP is not charged to the justice due to lack of proofs.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can move the protocol forward to the step 3, where if the
  SP follow the protocol then the customer can push the protocol forward
  up to the last termination step \(\sigma_{7, c, \mathrm{n}} = +\),
  otherwise if at any step the SP does not follow the protocol the
  customer can start a dispute which terminates the protocol at
  non-disadvantaged position, i.e.,
  \(\sigma_{3, c, \overline{\mathrm{d}}} = \sbullet\),
  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\),
  \(\sigma_{5, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{2, s, \mathrm{n}} = +\), \(\sigma_{2, s, \mathrm{d}} = +\),
  \(\sigma_{2, s, \overline{\mathrm{n}}} = \sbullet\),
  \(\sigma_{2, s, \overline{\mathrm{d}}} = \sbullet\).
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \mathrm{n}} = -\), the customer hasn't received the
    results so he remains in disadvantaged position.
  \item
    \(\sigma_{3, s, \mathrm{n}} = +\), the SP has fulfilled the contract
    on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \mathrm{d}} = -\), the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe.
  \item
    \(\sigma_{3, s, \mathrm{d}} = +\), the SP win the case for the same
    reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{n}}} = -\), the customer ends up in disadvantaged position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{n}}} = +\), the SP ends up in
    advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{3, c, \overline{\mathrm{d}}} = •\), the customer wins the case and end up in neutral position.
  \item
    \(\sigma_{3, s, \overline{\mathrm{d}}} = -\), the SP loses the case
    and end up in disadvantaged position.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \mathrm{n}} = -\), the customer hasn't received the results so he remains in disadvantaged position.
  \item
    \(\sigma_{4, s, \mathrm{n}} = +\), the SP has fulfilled the contract on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \mathrm{d}} = -\), the customer lose the case as the
    SP has still opportunity to publish proof-of-provision within
    timeframe.
  \item
    \(\sigma_{4, s, \mathrm{d}} = +\), the SP win the case for the same
    reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{n}}} = -\), the customer ends up in
    disadvantaged position.
  \item
    \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), the SP ends up in
    advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{4, c, \overline{\mathrm{d}}} = •\), the customer wins the
    case and end up in neutral position.
  \item
    \(\sigma_{4, s, \overline{\mathrm{d}}} = -\), the SP loses the case
    and end up in disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will
  ultimately put him in advantaged position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case of the SP not following
  the protocol, the customer can start a dispute and terminate in
  non-disadvantaged position
  \(\sigma_{4, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{4, s, \mathrm{n}} = +\), or not follow the protocol
  and also end up at non-disadvantaged position
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), but the second option
  puts him at risk of terminating the protocol at
  \(\sigma_{4, s, \overline{\mathrm{n}}} = +\), if the customer is
  rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \mathrm{n}} = -\) the customer hasn't received the
    results. Therefore, he remains in disadvantaged position.
  \item
    \(\sigma_{5, s, \mathrm{n}} = +\) the SP has fulfilled the contract
    on time.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{5, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{n}}} = -\) the customer ends up in disadvantaged position.
  \item
    \(\sigma_{5, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{5, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position.
  \item
    \(\sigma_{5, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \mathrm{n}} = -\) the customer gets hash of the
    results but not the results yet.
  \item
    \(\sigma_{6, s, \mathrm{n}} = +\) the SP position hasn't changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{6, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{n}}} = -\) the customer ends up in
    disadvantaged position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{n}}} = +\) the SP ends up in
    advantaged position as he received the payment but didn't spend his
    resources.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\sigma_{6, c, \overline{\mathrm{d}}} = •\) the customer wins the
    case and end up in neutral position.
  \item
    \(\sigma_{6, s, \overline{\mathrm{d}}} = -\) the SP loses the case
    and end up in disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position
  \(\sigma_{6, c, \mathrm{n}} = -\), which let's him move the protocol
  to non-disadvantaged termination position
  \(\sigma_{7, c, \mathrm{n}} = +\), or in case the SP haven't followed
  the protocol start a dispute and win the case
  \(\sigma_{6, c, \overline{\mathrm{d}}} = \sbullet\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{6, s, \mathrm{n}} = +\), or
  \(\sigma_{6, s, \overline{\mathrm{n}}} = +\).
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \mathrm{n}} = +\) the customer gets the correct
    results. Therefore, he moves to advantaged position.
  \item
    \(\sigma_{7, s, \mathrm{n}} = +\) the SP position hasn't changed.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \mathrm{d}} = -\) the customer lose the case as the
    SP can prove the publication of proof-of-provision.
  \item
    \(\sigma_{7, s, \mathrm{d}} = +\) the SP win the case as the SP can
    prove the publication of proof-of-provision.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = -\) customer end up in disadvantaged position, as he ends up with incorrect results.
  \item
    \(\sigma_{7, c, \overline{\mathrm{n}}} = +\) SP ends up in advantaged
    position as he received the payment but didn't spend his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = •\) customer wins the case and ends up in neutral position.
  \item
    \(\sigma_{7, c, \overline{\mathrm{d}}} = -\) SP lose the case and end up in disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\section{Future work}\label{sec:future-work}
\subsection{Justice}\label{justice}

@@

\section{Conclusions}\label{sec:conclusion}
In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision. The framework can be employed by any local service provider to provide services without collecting any personal information. The payment is handled by anonymous cryptocurrencies. Proof of delivery and proof of provision are published on message board blockchain. The results are published on content addressable p2p network. The dispute can be settled by disclosing proofs to justice. Assuming the definition~\ref{fairness} we showed that the protocol achieve fairness. Finally, we pinpointed further improvements like decentralised dispute resolution, provable  availability of results, paying with cash, and anonymous delivery via courier.
